
\begin{frame}
    \frametitle{Text pattern matching}
    \begin{itemize}
        \item Regular expressions (regex) are rules for the set of
        possible strings to match.
        \item Use regex to search and extract substrings.
        \item Set might contain words, whole sentences, or e-mail
        addresses, or anything you like.
        \item Are there matches for the pattern anywhere in the string?
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Regular Expression Syntax}
    \begin{itemize}
        \item \mintinline{bash}{.} matches any character except a newline.
        \item \mintinline{bash}{^} matches the start of the string.
        \item \mintinline{bash}{$} matches the end of the string.
        \item \mintinline{bash}{*} match 0 or more repetitions of the preceding RE.
        \item \mintinline{bash}{+} match 1 or more repetitions of the preceding RE.
        \item \mintinline{bash}{?} match 0 or 1 repetitions of the preceding RE.
    \end{itemize}

    See: \href{https://www.dataquest.io/wp-content/uploads/2019/03/python-regular-expressions-cheat-sheet.pdf}{Python regex cheat sheet}
\end{frame}

\begin{frame}[fragile]
    \frametitle{Text pattern matching --- Example}
\begin{minted}{python}
import re

# Find all href tags with http(s) link
re.findall('href="https?://.*?"', html)

# Find all href tags with http(s) link and return links only
re.findall('href="(https?://.*?")', html)

# Find all href tags with http(s) link and split
links_parts = re.findall('href="(https?)://(.*?)"', html)
[x[0] for x in links_parts]
[x[1] for x in links_parts]

# Find all prices
prices = re.findall('(\\d+(\\.?\\d+)*,?\\d*\\s€)', html)
prices = [x[0] for x in prices]
prices

# Clean up all prices
prices_clean = [re.sub('[^(\\d,)]', '', x) for x in prices]
prices_clean
\end{minted}
\end{frame}